%-------------------------
% Cover Letter in Latex
% Based on resume template
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Christian Wilkins} \\ \vspace{1pt}
    \small \href{mailto:christian.wilkins.careers@gmail.com}{christian.wilkins.careers@gmail.com} $|$
    \href{https://www.linkedin.com/in/christian--wilkins/}{linkedin.com/in/christian--wilkins/} $|$
    \href{https://github.com/christianwilkins}{github.com/christianwilkins} $|$
    \href{https://chriswiki.com/}{chriswiki.com}
\end{center}

\vspace{0.7in}

\noindent
\today

\vspace{0.5in}

\noindent
Dear OpenAI Hiring Team,

\vspace{0.4in}

I am writing to express my strong interest in the Software Engineer (Emerging Talent) position on the Applied Engineering team. OpenAI's mission to ensure that artificial general intelligence benefits all of humanity deeply resonates with me, and I am excited about the opportunity to contribute to technology that transcends geographic, economic, and platform barriers.

\vspace{0.2in}

Throughout my internships and projects, I have consistently focused on building AI solutions that solve real user problems. At JPMorganChase, I developed an AI-powered matching engine using scikit-learn and spaCy that won first place in their Global Hackathon out of 1000+ participants—not just for its technical merit, but because it addressed genuine employee pain points in job placement. This experience taught me the importance of understanding user needs deeply before building solutions, a principle I see reflected in OpenAI's approach to product development.

\vspace{0.2in}

Your emphasis on ``iterative, collaborative, fast-paced'' development aligns perfectly with my working style. During my research at Michigan State, I built ML pipelines for medical exam grading while collaborating closely with medical professionals to ensure our AI solutions met real-world deployment requirements. Similarly, at Configura, I navigated a 75M+ line codebase while proactively engaging senior engineers and clients daily—experiences that prepared me for the ambiguous, rapidly evolving environment where OpenAI operates.

\vspace{0.2in}

What excites me most about this role is the opportunity to work on customer-facing ChatGPT and OpenAI API features that reach millions of users worldwide. My full-stack experience with React, Next.js, and Python, combined with my direct experience integrating OpenAI APIs in projects like Notelify (which won ``Best Use of AI''), positions me well to contribute immediately to your frontend and backend systems. I've also worked extensively with PostgreSQL and other databases, understanding the importance of optimizing applications for speed and scale.

\vspace{0.2in}

OpenAI's commitment to safety and responsible AI deployment particularly resonates with me. In my research work processing HIPAA-compliant data, I learned firsthand how critical it is to handle sensitive information responsibly while still extracting meaningful insights. I believe AI's transformative potential comes with the responsibility to ensure it's developed and deployed safely—a value I'm eager to uphold as part of your team.

\vspace{0.2in}

I'm drawn to OpenAI not just for its cutting-edge technology, but for its culture of diverse perspectives and inclusive collaboration. Having led a 550-member organization and mentored 60 students across 10 development teams, I understand how diverse viewpoints strengthen both products and teams. I'm excited to contribute to a culture that ``makes all feel welcome'' while working on technology that will shape humanity's future.

\vspace{0.2in}

Thank you for considering my application. I would welcome the opportunity to discuss how my passion for AI, technical skills, and collaborative approach can contribute to OpenAI's mission of ensuring AGI benefits everyone.

\vspace{0.5in}

\noindent
Best regards, \\

\vspace{0.3in}

\noindent
Christian Wilkins

\end{document}