%-------------------------
% Tailored Resume: Rilla - Software Engineer
% Source facts: master-resume.tex
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \textbf{#1} \hfill #2 \\
  \textit{\small#3} \hfill \textit{\small #4} \\
  \vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \small#1 \hfill #2 \\
  \vspace{-7pt}
}

\renewcommand\labelitemii{\textbullet}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Christian Wilkins} \\ \vspace{1pt}
    \small \href{mailto:christian.wilkins.careers@gmail.com}{christian.wilkins.careers@gmail.com} $|$
    \href{https://www.linkedin.com/in/christian--wilkins/}{linkedin.com/in/christian--wilkins/} $|$
    \href{https://github.com/christianwilkins}{github.com/christianwilkins} $|$
    \href{https://chriswiki.com/}{chriswiki.com}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Michigan State University}{December 2025}
      {Bachelor of Science in Computer Science, Minor in Business - GPA 3.9}{East Lansing, MI}
  \resumeSubHeadingListEnd

\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript, Python, Java, C++, SQL, Dart, Golang} \\
     \textbf{Technologies}{: React, React Native, Node.js, PostgreSQL, Supabase, AWS, Docker, Linux, Git, GitHub Actions, Flask, Firebase} \\
     \textbf{Concepts}{: Full Stack Development, API Design, CI/CD, Contract Testing, Distributed Systems, AI/ML} }}
 \end{itemize}

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Contract Full Stack Developer}{November 2025 -- February 2026}
      {Paira Technologies LLC}{Remote}
    \resumeItemListStart
      \resumeItem{Owned end-to-end delivery across \textbf{React Native}, \textbf{Expo}, \textbf{Supabase}, and \textbf{Railway}, turning an early prototype into a production-ready iOS MVP.}
      \resumeItem{Built core workflows across discovery, likes, matching, real-time chat, and push notifications with \textbf{Supabase Auth}, \textbf{PostgreSQL}, Realtime, and Edge Functions.}
      \resumeItem{Implemented first-, second-, and third-degree connection graph features that strengthened social discovery and improved retention loops.}
      \resumeItem{Set up CI/CD with \textbf{GitHub Actions} for lint, type-check, and tests, plus EAS TestFlight and Edge Function deploy pipelines.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer I}{February 2026 -- Present}
      {JPMorganChase}{Columbus, OH}
    \resumeItemListStart
        \resumeItem{Resolved a long-standing authentication and state-management defect in about two weeks, removing forced refresh loops and restoring reliable daily testing workflows.}
        \resumeItem{Stabilized session-state and token-handling flows across an internal web stack so auth remained consistent during long test sessions.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{June 2025 -- August 2025}
      {JPMorganChase}{Columbus, OH}
    \resumeItemListStart
        \resumeItem{Built an AI-powered matching engine with scikit-learn, spaCy, and PostgreSQL for internal mobility workflows; project won first place in a global hackathon with 1000+ participants.}
        \resumeItem{Optimized AWS S3 migration concurrency by 95\% in Python with boto3 and concurrent.futures, reducing migration bottlenecks in production workflows.}
        \resumeItem{Implemented PactFlow contract testing across services, reducing cross-team integration issues by 90\%.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{May 2024 -- August 2024}
      {Configura}{Grand Rapids, MI}
      \resumeItemListStart
        \resumeItem{Shipped a client-facing extension in a 75M+ line proprietary codebase, partnering with senior engineers to deliver features in an undocumented environment.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Autonomous RC Crash Data Platform (MSU Capstone)} $|$ \emph{React, Flask, ROS2 Humble, UDP, Wi-Fi Networking}}{Fall 2025}
          \resumeItemListStart
            \resumeItem{Built a web app that controlled an RC vehicle and replayed telemetry, integrating Flask services with UDP messaging and ROS2 for repeatable crash-data experiments.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\underline{\textbf{\href{https://www.notelify.co/}{Notelify}}} $|$ \emph{Next.js, React, TypeScript, Python}}{October 2023 -- April 2024}
          \resumeItemListStart
            \resumeItem{Built an AI-powered note-taking platform with speech-to-text and summarization workflows, reducing manual note effort by 95\% in pilot usage.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}
